Market Expectations and Mangerial Turnover

### 2024-03-05 paper.qmd
updating the LLM work

data_helper <- spells |>
  mutate(row_id=row_number()) |>
  filter(is.na(Finish)&contract_expiry!="-") |>
  select(contract_expiry, Finish,row_id)
data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
spells |>
  mutate(row_id=row_number()) |>
  left_join(data_helper |> select(-Finish), by="row_id") |>
  mutate(Start = as.Date(Start),
         Finish = as.Date(Finish)) |>
  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
spells |> distinct(name,club,Finish) |> nrow()
# find duplicates for name,club,Finish
spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
# remove duplicates
spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) -> spells
spell <- spells |> select(club,Start,Finish) |> arrange(Finish)
spell |> filter(Finish-Start>0) -> spell
```

@@

- `name`: The name of the person in charge
- `club`: The club the manager was in charge of
- `position`: The position of the person in charge
- `Start`: The start date of the spell
- `Finish`: The end date of the spell
- `days_in_charge`: The number of days the manager was in charge of the club
- `season_start`: The start of the season the spell ended

```{r}
#| label: fig-annual-spell-count
#| fig-cap: "Annual count of manager spell ending"
library(ggplot2)
library(dplyr)
# create plot of annual count of spells using a count of finishes per season assume season starts in August
spell |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
  count(season_start) |> 
  ggplot(aes(x = season_start, y = n)) +
  geom_col(width = 0.5) +
  labs(title = "Annual count of spell ending", x = "Season", y = "Number of spells") +
  theme_minimal() -> spell_count
plotly::ggplotly(spell_count)
```

@@

```{bash}
#!/bin/bash

# Define a function to make an HTTP request to the API and parse the response
function api_call() {
  local club_name="$1"
  local year_end_of_season="$2"
  local response=$(curl -s -H "Content-Type: application/json" \
    --data '{"model": "llama2", "prompt": "Which country is the club 
${club_name} from? What is its division level based on the year 
${year_end_of_season}?"}' http://localhost:11434/api/generate)
  echo "Processing club ${club_name} (${year_end_of_season})"
  echo "${response}" >> responses.csv
}

# Read the input CSV file with clubs and end of season dates using csvparse
input_file="input.csv"
output_file="output.csv"
IFS=$'\n'
mapfile -t clubs < <(csplit ${input_file} '{printf "%s\n" %${0}}}')
unset IFS
declare -a clubs_array=(${clubs[@]})
declare -a years_array=()
for i in $(seq 0 ${#clubs_array[*]}-1); do
  IFS=',' read -r club_name year < "${input_file}" || continue
  years_array+=("${year}")
done
unset IFS

# Loop over the clubs and call the API for each one with its respective end 
of season year
for ((i = 0; i < ${#clubs_array[@]}; i++)); do
  local club_name="${clubs_array[$i]}"
  local year="${years_array[$i]}"
  api_call "${club_name}" "${year}"
done

echo "Done processing all clubs. Total responses processed: $(wc -l < 
responses.csv)"
```

>>>>

data_helper <- spells |>
  mutate(row_id=row_number()) |>
  filter(is.na(Finish)&contract_expiry!="-") |>
  select(contract_expiry, Finish,row_id)
data_helper$Finish<-as.Date(map_dbl(data_helper$contract_expiry, season_to_date))
spells |>
  mutate(row_id=row_number()) |>
  left_join(data_helper |> select(-Finish), by="row_id") |>
  mutate(Start = as.Date(Start),
         Finish = as.Date(Finish)) |>
  mutate(days_in_charge = as.numeric(Finish - Start)) ->spells
# find duplicates for name,club,Finish
#spells |> drop_na(Start,Finish) |> group_by(name,club,Finish) |> summarise(n=n()) |> filter(n>1) |> arrange(desc(n))
# remove duplicates
spells |> drop_na(Start,Finish) |> distinct(name,club,Finish,.keep_all = TRUE) |> filter(Finish-Start>0) -> spells

@@

-   `name`: The name of of staff member
-   `club`: The club of the staff member
-   `position`: The position of the staff member
-   `appointed`: The start date of the spell
-   `contract_expiry`: The end date of the spell
-   `days_in_charge`: The number of days the manager was in charge of the club
-   `wins`: Number of wins for spell
-   `draws`: Number of draws for spell
-   `losses`: Number of losses for spell
-   `players_used`: Number of players used in the spell
-   `avg_goals_for`: Average goals scored per game
-   `avg_goals_against`: Average goals conceded per game
-    `ppm`: Points per match

```{r}

```{r}
#|label: tbl-managertype
#| tbl-cap: "Manager types"
library(kableExtra)
terms_to_remove <- c("1.FC Köln II","Al-Ahli (UAE)","Gimnasia (J)","San Martín (T)",
  "San Martín (SJ)","Racing (Cba)","Juv. Unida (G)","1.FC Köln U19",
  "1.FC Köln U17","1.FC Köln Yth.",
  "1.FC Köln U16"," II","1.FC Köln","Bor. M'gladbach",
  "Hertha BSC","F. Düsseldorf",
  "Velez Mostar","SSV Reutlingen","FV Ravensburg",
  "Fenerbahce","FC Teningen","FV Nimburg","Heart of Midl.",
  "Vetra","Sp.Genzano (PZ)","Honvéd FC","Olympiacos","Honvéd SE","Hungary",
  "ADO Den Haag(A)","Dordrecht'90","Haarlem","AZ Alkmaar","Roda JC","AZ '67",
  "Sparta R.","De Treffers","NEC Nijmegen","FC Oss","VV Gemert","PSV U21")
spells %>%
  mutate(position = str_remove_all(position, paste0("(", paste(terms_to_remove, collapse = "|"), ")"))) -> spells
spells |> mutate(
    staff_position = trimws(tolower(position)),
    staff_position = ifelse(staff_position=="manager","manager",staff_position),
    staff_position = ifelse(staff_position=="assistant manager","assistant manager",staff_position),
    staff_position = ifelse(staff_position=="caretaker manager","caretaker manager",staff_position),
    staff_position = ifelse(str_detect(staff_position,"player-coach"),"player-coach",staff_position),
    staff_position = ifelse(str_detect(staff_position,"director of football"),"director of football",staff_position),
    staff_position = ifelse(str_detect(staff_position,"technical director"),"technical director",staff_position),
    staff_position = ifelse(str_detect(staff_position,"director of professional football"),"director of professional football",staff_position),
    staff_position = ifelse(str_detect(staff_position,"sporting director"),"sporting director",staff_position),
    staff_position = ifelse(str_detect(staff_position,"academy manager"),"academy manager",staff_position),
    staff_position = ifelse(str_detect(staff_position,"advisor"),"advisor",staff_position),
    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position),
    staff_position = ifelse(str_detect(staff_position,"head of football operations"),"head of football operations",staff_position)) %>%
  {table(.$staff_position[!is.na(.$staff_position)])} |> sort(decreasing = TRUE) |> 
  # make the frequency table into a data frame
  as.data.frame() |>
  # rename the columns
  rename("staff_position" = "Var1", "n" = "Freq") |>
  # order the data frame by the frequency
  arrange(desc(n)) |>
  head(20) |>
  kable(col.names=c("Staff Role","Number")) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F)
```

```{r}
#| label: fig-annual-spell-count
#| fig-cap: "Annual count of manager spell ending"
library(ggplot2)
library(dplyr)
# create plot of annual count of spells using a count of finishes per season assume season starts in August
spells |> mutate(season_start = ifelse(month(Start) < 8, year(Start), year(Start) + 1)) |> 
  count(season_start) |> 
  ggplot(aes(x = season_start, y = n)) +
  geom_col(width = 0.5) +
  labs(title = "Annual count of spell ending", x = "Season", y = "Number of spells") +
  theme_minimal() -> spell_count
plotly::ggplotly(spell_count)
```

@@
